\section{Introduction}

%% The importance of magnetization direction and techniques
Most  magnetic methods require knowledge of the magnetization direction, and otherwise 
yield unsatisfactory interpretations of the exploration targets. This fact has 
propelled the development of several techniques for estimating magnetization 
direction over the last 50 years. Strategies for estimating this quantity can be 
divided into two main groups. The first one comprises the methods that presume a prior 
information about the shape of geological sources. The iterative method presented by 
\cite{bhattacharyya1966} presumes that the magnetic source has a rectangular prismatic shape. 
\cite{emilia_massey_1974} approximate a seamount by a set of stacked 
prisms with uniform magnetization direction and variable magnetization intensity. 
\cite{parker_etal_1987} represent the geometry of a seamount by using a 
covering of triangular facets and estimate the internal magnetization closest to 
a uniform solution.
\cite{medeiros_silva_1995} present a method that estimates the total magnetization 
direction and the spatial orientation of an isolated source having three orthogonal planes of 
symmetry. 
\cite{kubota2005} also approximate a seamount by a set of juxtaposed prisms, but estimate a 
magnetization direction for each one. 
Finally, \cite{oliveirajr_etal_2015} approximate the magnetic sources by spherical bodies with 
known centers for estimating their magnetization directions. 

The second group is formed by methods that do not presume any information about the shape of the 
magnetic sources. \cite{fedi_etal_1994}, for example, propose a method that determines the best 
magnetization direction among a set a tentative values used to perform 
successive reductions to the pole in the Fourier domain. 
\cite{phillips2005} uses the Helbig's integral for estimating the components of the magnetic-moment vector. 
\cite{tontini_pedersen_2008} extend the Phillips' method by using the same Helbig's integral 
to estimate the magnetization direction and its magnitude, also providing information about the position 
of the center of magnetization distribution. \cite{lelievre_oldenburg_2009} develop a method for estimating 
the magnetization direction in complex geological scenarios. Their method approximates the subsurface 
by a grid of juxtaposed prisms and estimates the components of the magnetization vector for each prism.
In addition, there are methods based on the correlation of potential-field quantities \citep[e.g.,][]{dannemiller_li_2006,gerovska_etal_2009,liu_etal_2015,zhang_etal_2018,
ribeiro_filho_etal2020}.

%%The equivalent layer 
Estimating the magnetization direction is extremely important not only for interpretation, 
but also for processing the total-field anomaly data. One technique in the spatial domain 
commonly used for processing potential-field data is the equivalent layer. It was first introduced 
in exploration geophysics by \cite{dampney1969} and \cite{emilia_massey_1974} for processing 
gravity and magnetic data, respectively. After these pioneer works, this technique has been widely 
used for computing interpolation \citep{cordell_1992, mendonca-silva_1994, barnes-lumley_2011, siqueira_etal_2017}, 
upward (or downward) continuation  \citep{cribb1976, hansen-miyazaki_1984, li-oldenburg_2010, mastellone_etal_2014}, reduction to the pole 
\citep{silva_1986, leao-silva_1989, guspi-novara_2009, oliveirajr-etal_2013}, the amplitude of 
anomalous field \citep{li_li_2014} and for denoising gradient data \citep{martinez_li_2016}. 
The equivalent-layer technique consists in approximating the observed data by those produced by a 
layer of discrete sources (e.g., prisms, dipoles or point masses), which are commonly known as 
equivalent sources. The data produced by this fictitious layer (the equivalent layer) are commonly
called predicted data.

%%  positivity constraints 
In scanning magnetic microscopy, the equivalent-layer technique is generally used for interpreting 
the magnetic-moment distribution within thin planar sections of rock samples. Note that, in this case, 
the equivalent layer resembles the true source (a thin section of rock). 
\cite{weiss2007} present one of the first works using the equivalent-layer technique in scanning magnetic microscopy.
They point out without proof that the estimated magnetic-moment distribution on the layer is all-positive when  
the magnetization direction of the equivalent sources is equal to that used for artificially magnetizing the rock sample. 
\cite{baratchart2013} show mathematically that, assuming a uniform magnetization direction within the thin section, 
the inverse problem of estimating the magnetic-moment distribution has a unique solution. 
\cite{lima2013} propose a method on the frequency domain to investigate solutions having a uniform magnetization 
direction equal to that of a thin section of geological sample. They show empirically 
that, in this case, the estimated magnetic-moment distribution on the layer is entirely positive. 

In the geophysical exploration, the equivalent-layer technique is predominantly used for processing potential-field data. 
Under this perspective, there is no relationship between the physical-property distribution on the equivalent layer 
and the true geological sources. Hence, the layer is just a mathematical abstraction devoid of geological meaning. 
Few authors in geophysical exploration literature have been addressed the use of the equivalent-layer technique for interpreting
the geological sources. \cite{pedersen1991}, for example, discusses the relationship between potential field and equivalent source. 
\cite{medeiros_silva1996} and \cite{silva-etal2010} estimate an apparent-magnetization map on a layer by using Tikhonov and 
entropic regularizations respectively. \cite{siqueira_etal_2017} establish a relationship between the excess of mass estimated 
over the equivalent layer and the true one. \cite{li_etal_2014} prove, by using a Fourier-domain  approach, 
the existence of an all-positive magnetic-moment distribution over the layer and use this to overcome the reduction to the pole low-latitude instability. 
However, this work considers only the particular case in which the magnetic sources have a purely induced magnetization.

%% Joining techniques for estimating the magnetization direction 
Here, we prove mathematically that there exists an all-positive magnetic-moment 
distribution within the equivalent layer even in the 
presence of geological sources with remanent magnetization. This all-positive 
magnetic-moment distribution exists for 
all cases in which the magnetization directions of the equivalent sources have the 
same orientation as that of the true geological sources, 
regardless of whether the magnetization of the true sources is purely induced 
or not. Grounded on this generalized positivity constraint, 
we present a new iterative method that uses the equivalent-layer technique 
for estimating the uniform magnetization direction of 
arbitrary sources by inverting total-field anomaly data. Our method does not 
presume any information about the shape of the sources. 
At each iteration, our method solves (1) a linear inverse problem, subject to 
a positivity constraint, for estimating the magnetic-moment 
distribution within a planar equivalent layer of dipoles, and (2) a 
non-linear inverse problem for estimating the uniform magnetization 
direction of the equivalent sources. Tests with synthetic data generated 
by different geological scenarios show that the estimated magnetization
direction converges to that of the true sources. We also applied our method to 
field data from the Goi{\' a}s alkaline province (GAP), 
over the Montes Claros complex, center of Brazil. Our results are in agreement 
with those obtained independently by \cite{zhang_etal_2018} 
in the same area, suggest the presence of a remarkable remanent magnetization 
and show the good performance of our method in interpreting 
a complex geological scenario.
