\section{Application to field data}
\label{sec:real_application}

The Goias alkaline province (GAP) is a region in the central part of Brazil that there are occurences of mafic-ultramafic alkaline magmatism. This region presents a variety of rocks with an extense petrographic types. Throughout the area there are mafic-ultramagic complexes (plutonic intrusions), subvolcaninc alkaline intrusions (diatremes) and volcanic products (kamafugite lava flows) with several dikes. Among the main alkaline complexes of GAP are the Montes Claros de Goias, Diorama, Corrego dos Bois, Morro do Macaco and Fazenda Buriti. These alkaline intrusions are sorrounded by a Precambrian basement and the Phanerozoic sedimentary rocks of the Paraná basin. \citep{junqueira_brod_2005,carlson_etal_2007,marangoni_mantovani_2013,dutra_etal_2014}. Recent studies indicate the existence of a remarkable remanent magnetization component within these intrusions \citep{marangoni_mantovani_2013,oliveirajr_etal_2015,marangoni_etal_2016,zhang_etal_2018}. 

This area was the target of an aeromagnetic survey with a financial support from the government of the state of Goias (LASA Prospection and Engineer, 2004). This survey has a flight pattern with North-South spaced from $\sim 500 \, m$ and $ \sim 8 \, m$ along each line, and a constant height of $100 \, m$ from the terrain. The main field direction for this area was $-19.5^\circ$ and $-18.5^\circ$ for inclination and declination, respectively. In order to test the methodology on a field data, we invert the data from the alkaline complex of Montes Claros. To speed up data processing and inversion, we downsampled the data along the flight lines, resulting a grid of $55 \times 32$ points (a total of $N=1787$ observations). This new set up results an approximately $320 \, m$ and $470 \, m$ grid spacing along the x- and y-axis, respectively. Figure \ref{fig:mc_data_application}a shows the observed data from the complex of Montes Claros. For the inversion, we use an equivalent layer composed by a grid of $55 \times 32$ dipoles (a total of $M=1787$ equivalent sources) positioned at a depth of $840 \, m$ below the observation plane ($\sim 2$ times the greater grid spacing). The algorithm \ref{cd: LM_NNLS} starts with an initial guess of $-70^\circ$ and $50^\circ$ for the inclination and declination, respectively. Figure \ref{fig:mc_data_application}b shows the predicted data produced by equivalent layer. Figure \ref{fig:mc_data_application}c shows the residuals defined as the difference between the observed data (figure \ref{fig:mc_data_application}a) and the predicted data (figure \ref{fig:mc_data_application}b). The histogram of residuals (figure \ref{fig:mc_data_application}d) presents a mean of $-14.52 \, nT$ ($\sim 0.1\% $ of the maximum value of total-field anomaly data) and standard deviation of $312.28 \, nT$ ($\sim 2 \% $ of the maximum value of total-field anomaly data). The estimated magnetization direction $\mathbf{q}^\sharp$ has inclination $-50.2^\circ$ and declination $34.9^\circ$. Figure \ref{fig:mc_data_application}e shows the estimated magnetic-moment distribution $\mathbf{p}^\sharp$. The convergence of the algorithm \ref{cd: LM_NNLS} is shown in figure \ref{fig:mc_data_application}f. We check the quality of the estimated magnetization direction by computing the reduction-to-pole of the observed total-field anomaly. Figure \ref{fig:rtp_mc_data} shows the RTP anomaly. As we can notice from this last figure is that the RTP field exhibits predominantly positive values and decays to zero towards the borders of study area. For this reason, we consider that the estimated magnetization direction led to a satisfactory RTP anomaly. We conclude with these results that the all-positive magnetic moment distribution and the estimated magnetization direction produce an acceptable data fitting. The estimated magnetization direction also confirms the existence of remarkable remanent magnetization for these instrusions. 


